Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-28 mu/article/article.tex
Cheking lost fig.
Up first energy rane description completed.

@@

145^{\circ}$. In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 

@@

$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)fixing
the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the
photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (left scale). Also in the bottom frames of Figs. 
\ref{fig:alt-vx-comp-rtp} and
\ref{fig:alt-vy-comp-rtp} we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and 
$|\mathcal{V}^{\mathrm{y}}|$ 
in the corresponding components
$\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xz}}$ and
$\mathcal{V}^{\mathrm{yy}}$
with $\alpha$ fixed to $145^{\circ}$.

@@

velocity magnitude $|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s being this the
absolute maximum fixing the spin-velocity in the $x$ direction. Then, the
components give us polar and azimuthal angles with values of

@@

direction. This is due to a change in the spin polarization direction. Finally after the enrgy value of 0.886\,eV the response decreases and goes to zero. 

@@

\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV the $yz$ component have a major contribution than the $yx$ and $yy$ components having values of 

@@

and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and $\theta=221.6^{\circ}$, respectively.

@@

Also, for an energy of the incoming beam of 0.912\,eV we found that the contribution of the components are 

@@

@@

% %% 0.0 eV - 0.16 eV
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    \label{fig:up-vab-comp-rtp-1}
% %% 0.0 eV - 0.16 eV

@@

$45^{\circ}$ is the zone of the maximum response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 

@@

@@

In Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present
the results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
angles. In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and 
\ref{fig:up-vx-comp-rtp-1} we present the decomposition of
corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$ and
$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $40^{\circ}$. From
Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with energy of
0.088\,eV the three components have similar contributions and have values of
$\mathcal{V}^{\mathrm{xx}}= -36.5$\,Km/s,
$\mathcal{V}^{\mathrm{xz}}=39.8$\,Km/s resulting in a value of
$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s and corresponding to polar and azimuthal
angles of $\varphi=47.4$ and $\theta=212.5$, respectively.
the same incoming beam energy have values of $\mathcal{V}^{\mathrm{yx}}=
-7.9$\,Km/s $\mathcal{V}^{\mathrm{yy}}= 8.5$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s resulting in a value of the total
response of $|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal
angles $\varphi=7.6$ $\theta=132.7$, respectively.

>>>>

\textbf{Alt structure.}

@@

145^{\circ}$. 
In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 

@@

$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs
the photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). Also in the bottom frames of Figs. 
\ref{fig:alt-vx-comp-rtp} and \ref{fig:alt-vy-comp-rtp} we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
in the corresponding components $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
$\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$
$\mathcal{V}^{\mathrm{yz}}$ with $\alpha$ fixed to $145^{\circ}$.

@@

velocity magnitude 
$|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s 
being this the absolute maximum fixing the spin-velocity in the $x$ direction.
Then, the components give us polar and azimuthal angles with values of

@@

direction. This is due to a change in the spin polarization direction. Finally
after the energy value of 0.886\,eV the response decreases and goes to zero.

@@

\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV
the $yz$ component have a major contribution than the $yx$ and $yy$ components
having values of

@@

and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and
$\theta=221.6^{\circ}$, respectively.

@@

Also, for an energy of the incoming beam of 0.912\,eV we found that the
contribution of the components are

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{alt} structure.}
    \label{fig:alt-vyz-lay}

@@

\textbf{Up structure.}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

@@

$45^{\circ}$ is the zone where the maximum responses for both,
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
\ref{fig:up-vy-comp-rtp-1} we present the results for
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
angles (right scale). In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1}
and \ref{fig:up-vx-comp-rtp-1} we present the decomposition of
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yy}}$,
components with $\alpha$ fixed to $40^{\circ}$. 

@@

% %% Description of UP |V^{a}|, components and RTP
% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
From Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with
energy of 0.088\,eV the three components have similar contributions and have
values of 
$\mathcal{V}^{\mathrm{xx}}=-36.5$\,Km/s,
$\mathcal{V}^{\mathrm{xz}}= 39.8$\,Km/s 
resulting in a value of
$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s 
being this value the absolute maximum obtained when the spin-velocity is fixed
in the $x$ direction. To this value corresponds a polar and azimuthal angles of
$\varphi=47.4$ and $\theta=212.5$, respectively.
the same incoming beam energy have values of 
$\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s 
$\mathcal{V}^{\mathrm{yy}}=  8.6$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}= 87.2$\,Km/s 
resulting in a value of the total response of
$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s
being this value the absolute maximum obtained when the spin-velocity is fixed
in the $y$ direction and being 1.5 times more intense than
$|\mathcal{V}^{\mathrm{x}}|$ and corresponding spin polar and azimuthal angles
$\varphi=7.6$ $\theta=132.7$, respectively. We also found that since the onset
of the response till an energy for the incoming beam of 0.118\,eV the components
of both, $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have no
change in the spin polarization direction. Finally, after this energy value both
goes to zero.
% %% 1.80 eV - 2.10 eV

@@
